Can we explain the popularity of Netflix Shows?

### 2023-01-23 submission.Rmd
save work

query <- "SELECT netflixData.show_id
        , netflixData.type
        , netflixData.title
        , netflixData.director
        , netflixData.cast
        , netflixData.country
        , netflixData.date_added
        , netflixData.release_year
        , netflixData.rating
        , netflixData.duration
        , netflixData.listed_in
        , netflixData.description
        , googleData.Likes
        , googleData.Languages
        , googleData.Genres
        , googleData.Descriptions
        FROM netflixData left join googleData 
        ON netflixData.show_id= googleData.show_id"
res <- dbSendQuery(con, query)
df <- dbFetch(res)

@@

# Previewing Raw Data
## Renaming Columns
I rename the columns because some of them had the same names. 
Independent features that were scraped from Google have "google_" at the front of them.
``` {r}
new_names <- c("id" 
        , "type"
        , "title"
        , "director"
        , "cast"
        , "country"
        , "date_added"
        , "release_year"
        , "rating"
        , "duration"
        , "genre"
        , "plot"
        , "google_score"
        , "google_language"
        , "google_genre"
        , "google_plot")
df <- setNames(df, new_names)
```
## Data Preview
Here is what the dataset looks like now, we can see all the features that will be used:
``` {r echo=FALSE}
temp = head(df, 10)
temp %>%
  kbl() %>%
  kable_styling() %>%
  column_spec(1, width = "10cm") %>%
  scroll_box(width = "1000px", height = "500px")
```

@@

NA_Count <- c(
 toString(count_blanks('id'))
, toString(count_blanks('type'))
, toString(count_blanks('title'))
, toString(count_blanks('director'))
, toString(count_blanks('cast'))
, toString(count_blanks('country'))
, toString(count_blanks('date_added'))
, toString(count_blanks('release_year'))
, toString(count_blanks('rating'))
, toString(count_blanks('duration'))
, toString(count_blanks('genre'))
, toString(count_blanks('plot'))
, toString(count_blanks('google_score'))
, toString(count_blanks('google_language'))
, toString(count_blanks('google_genre'))
, toString(count_blanks('google_plot')))
NA_Count <- data.frame(feature, NA_Count)

@@

@@

### 4. Country
``` {r}
view <- df %>% group_by(country) %>% summarise(count = n())
print(view)
```
Some shows originated from several different countries.
Action: Similar to what will be done with the Director and Cast Feature, I will make mapping tables and use feature engineering to capture this variable.

### 5. Date Added
``` {r}
view <- df %>% group_by(date_added) %>% summarise(count = n())
print(view)
print(typeof(df$date_added))
```
Date Added is in the character format.
Action: Change this to date format
``` {r}
df$date_added <- mdy(df$date_added)
```

@@

### 9. Genre
``` {r}
view <- df %>% group_by(genre) %>% summarise(count = n()) # Show genre and count by each genre
print(view)
```
Some of the rows have more than one genre. 
Action: In the next Feature Engineering Section, I will make mapping tables and use feature engineering to capture this variable

@@

### Build Country Mapping Table
``` {r}

country_mapping <- df %>%
    mutate(country = strsplit(as.character(country), ",")) %>%
    unnest(country)

country_mapping = subset(country_mapping, select = c(id, country))
country_mapping$country <- trimws(country_mapping$country, which = c("left"))

write.csv(country_mapping, "datasets/mapping_country.csv", row.names=FALSE)
```

### Build Genre Mapping Table
``` {r}
genre_mapping <- df %>%
    mutate(genre = strsplit(as.character(genre), ",")) %>%
    unnest(genre)

genre_mapping = subset(genre_mapping, select = c(id, genre))
genre_mapping$cast <- trimws(genre_mapping$genre, which = c("left"))
write.csv(genre_mapping, "datasets/mapping_genre.csv", row.names=FALSE)
```

@@

Before carrying out further analysis, I disconnect from SQLite I write the main dataframe into a csv 
``` {r}
dbDisconnect(con)
write.csv(df, "datasets/view_main_cleaned.csv", row.names=FALSE)
```

@@

# Exploratory Data Analysis

### Corelation between numeric features
Before we get started, it would be useful to know how correlated the features are. I do this for the numeric features. 
``` {r}
numeric_features <-  select_if(df, is.numeric)
corr<- cor(numeric_features)
ggcorrplot(corr)
plot()
```

@@

>>>>

query <- "SELECT netflixData.show_id
        , netflixData.type
        , netflixData.title
        , netflixData.director
        , netflixData.cast
        , netflixData.country
        , netflixData.date_added
        , netflixData.release_year
        , netflixData.rating
        , netflixData.duration
        , netflixData.description
        , googleData.Likes
        , googleData.Languages
        , googleData.Genres
        , googleData.Descriptions
        FROM netflixData left join googleData 
        ON netflixData.show_id= googleData.show_id"
res <- dbSendQuery(con, query)
df <- dbFetch(res)

@@

# Previewing Raw Data
## Renaming Columns
I rename the columns because some of them had the same names. 
Independent features that were scraped from Google have "google_" at the front of them.
``` {r}
new_names <- c("id" 
        , "type"
        , "title"
        , "director"
        , "cast"
        , "country"
        , "date_added"
        , "release_year"
        , "rating"
        , "duration"
        , "plot"
        , "google_score"
        , "google_language"
        , "google_genre"
        , "google_plot")
df <- setNames(df, new_names)
```
## Data Preview
Here is what the dataset looks like now, we can see all the features that will be used:
``` {r echo=FALSE}
temp = head(df, 10)
temp %>%
  kbl() %>%
  kable_styling() %>%
  column_spec(1, width = "10cm") %>%
  scroll_box(width = "1000px", height = "500px")
```

@@

NA_Count <- c(
 toString(count_blanks('id'))
, toString(count_blanks('type'))
, toString(count_blanks('title'))
, toString(count_blanks('director'))
, toString(count_blanks('cast'))
, toString(count_blanks('country'))
, toString(count_blanks('date_added'))
, toString(count_blanks('release_year'))
, toString(count_blanks('rating'))
, toString(count_blanks('duration'))
, toString(count_blanks('plot'))
, toString(count_blanks('google_score'))
, toString(count_blanks('google_language'))
, toString(count_blanks('google_genre'))
, toString(count_blanks('google_plot')))
NA_Count <- data.frame(feature, NA_Count)

@@

``` {r}
missing.values <- df %>%
    gather(key = "key", value = "val") %>%
    mutate(is.missing = is.na(val)) %>%
    group_by(key, is.missing) %>%
    summarise(num.missing = n()) %>%
    filter(is.missing==T) %>%
    select(-is.missing) %>%
    arrange(desc(num.missing))

print(missing.values)
```

@@

### 4. Country
``` {r}
view <- df %>% group_by(country) %>% summarise(count = n())
print(view)
```
Some shows originated from several different countries. However, the countries seem to be in the order of influence.
Action: Take the first country on the list.

``` {r}
df$country <- sub("\\,.*", "", df$country)
```

### 5. Date Added
``` {r}
view <- df %>% group_by(date_added) %>% summarise(count = n())
print(view)
print(typeof(df$date_added))
print(df$date_added)

```
Date Added is in the character format.
Action: Change this to date format
``` {r}
#df$date_added <- mdy(df$date_added)
#print(df$date_added )
```

@@

@@

@@

Before carrying out further analysis, I disconnect from SQLite I write the main dataframe into a csv 
``` {r}
dbDisconnect(con)
print(head(df,10))

df = subset(df, select = -c(cast,director) )

write.csv(df, "datasets/view_main_cleaned.csv", row.names=FALSE)
```

@@

# Exploratory Data Analysis
# https://shopify.engineering/conducting-exploratory-data-analysis

### Feature Description

1. Type : Type of Netflix Show (Movie or TV Show)
2. Title: Name of the Netflix Show
3. Director : List of directors of the show
4. Cast: List of casts of the show
5. Country: List of countries relating to the show
6. Date Added: Date the show was put on Netflix
7. Release Year: Year the show was first released
8. Genre: List of genres of the show 
9. Plot: Description of the plot of the show
10. Google Score: Displayed on Google as the percentage of viewers that liked a show
11. Google Genre: Whether or not Genre is absent/present in the google search
12. Google Language: Whether or not Language is absent/present in the google search
13. Google Plot: Plot of the show according to Google
14. Duration Minutes: Duration of the movie in minutes
15. Duration Seasons: Durationg of the TV show in terms of how many seasons it has
16. Cast Points: Level of popularity of the most famous cast member of the show according to IMDB
17. Director Points: Level of popularity of the most famous director of the show according to IMDB
18. LSA category: Category of the show according to the LSA algorithm

Dependent Feature:
Google Score:

Independent Features:
Type, Date Added, Release Year, Google Genre, Google Language, Duration Minutes, Duration Seasons, Cast Points, Director Points, LSA Category

Features not directly for Analysis:
Title, Director, Cast, Country, Genre, Plot, Google Plot

### Among the Independent Features, What are the Categorical, discrete and continuous features

Categorical: Type, LSA Category

Discrete: Date Added, Release Year, Google Genre, Google Language, Duration Seasons

Continuous: Duration Minutes, Cast Points, Director Points

### Distribution of the features

1. Type
```{r}
ggplot(df, aes(x = type)) +  # Plot with values on top
  geom_bar() 
plot()
```
2. LSA

3. Date Added
```{r}
ggplot(df, aes(x = date_added)) +
    geom_density()
plot()
```

### Find outliers

### Significant Correlations

### Corelation between numeric features
Before we get started, it would be useful to know how correlated the features are. I do this for the numeric features. 
<!-- ``` {r}
numeric_features <-  select_if(df, is.numeric)
corr <- cor(numeric_features)
ggcorrplot(corr)
plot()
``` -->

@@

#
